Gammapy: A Python package for gamma-ray astronomy

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

\paragraph{Background model:}
The BKG can be represented in \gammapy as either 1) a 2D map (\code{Background2D})
of count rate normalised per steradians and energy at different
energies and offset-angles or 2) as rate per steradians and energy, as a
function of reconstructed energy and detector coordinates (\code{Background3D}).
In the former, the background is expected to follow a radially symmetric shape,
while in the latter, it can be more complex.

>>>>

\paragraph{Background model:}
The BKG can be represented in \gammapy as either 1) a 2D map (\code{Background2D})
of count rate normalised per steradians and energy at different
reconstructed energies and offset angles or 2) as rate per steradians and energy, as a
function of reconstructed energy and detector coordinates (\code{Background3D}).
In the former, the background is expected to follow a radially symmetric shape,
while in the latter, it can be more complex.
